### 2013-07-18 Tex/chapters/results.tex
corrections to scaling

    rather small value such that eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
    do not apply very good.\\

@@

    they are close enough to the expectations
    to be consistent. At least the expectations are always within two
    times the uncertainty.

@@

    systems (\(L=32,64\)) were used for the analysis, which introduce
    some deviations, because the collapse works best for big system sizes.

>>>>

    rather small value. Eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}
    are approximations for big \(L\). For small \(L\) one needs some
    \emph{corrections to scaling} terms, which are not considered here.\\

@@

    they are close enough to the expectations to be consistent. At least
    the expectations are always within two times the uncertainty.

@@

    systems (\(L=32,64\)) were used for the analysis, and no corrections
    to scaling terms were considered.
